Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-23 paper.qmd
Update hexgrid layout of remove low-density section

hex_grid_coloured_scurve1 <- ggplot() + 
  geom_point(data = umap_scurve_scaled, 
             aes(x = UMAP1, y = UMAP2), 
             alpha = 0.5,
             size = 0.5) + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve1, 
    aes(x = x, y = y,
      group = hex_poly_id, 
      fill = std_counts), color = "grey70", linewidth=0.2) +
  scale_fill_viridis_c(direction = -1, 
    na.value = "#ffffff", option = "C") +
  interior_annotation("a") +
  xlim(sc_xlims) + ylim(sc_ylims)
```

@@

hex_grid_coloured_scurve2 <- ggplot() + 
  geom_point(data = umap_scurve_scaled, 
             aes(x = UMAP1, y = UMAP2), 
             alpha = 0.5,
             size = 0.5) + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve2, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", 
        linewidth=0.2) +
  scale_fill_viridis_c(direction = -1, 
    na.value = "#ffffff", option = "C") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("b")

@@

hex_grid_coloured_scurve3 <-  ggplot() + 
  geom_point(data = umap_scurve_scaled, 
             aes(x = UMAP1, y = UMAP2), 
             alpha = 0.5,
             size = 0.5) + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve3, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", linewidth=0.2) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("c")

@@

hex_grid_rm_lwd_scurve1 <-  ggplot(
  data = hex_grid_with_counts_s_curve2, 
  aes(x = x, y = y)) + 
  geom_polygon(color = "black", aes(group = hex_poly_id, fill = std_counts)) +
  geom_text(data = hex_grid_with_low_counts, 
            color = "black", 
            aes(x = c_x, y = c_y, group = hex_poly_id, label = "X", size = 1)) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("a")
```

@@

hex_grid_rm_lwd_scurve2 <-  ggplot(
  data = hex_grid_with_counts_s_curve2, 
  aes(x = x, y = y)) + 
  geom_polygon(color = "black", aes(group = hex_poly_id, fill = std_counts)) +
  geom_text(data = hex_grid_with_low_counts_neighbor, 
            color = "black", 
            aes(x = c_x, y = c_y, group = hex_poly_id, label = "X", size = 1)) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("b")
```

>>>>

hex_grid_coloured_scurve1 <- ggplot() + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve1, 
    aes(x = x, y = y,
      group = hex_poly_id, 
      fill = std_counts), color = "grey70", linewidth=0.2) +
  geom_point(data = umap_scurve_scaled,
             aes(x = UMAP1, y = UMAP2),
             alpha = 0.3,
             size = 0.5) +
  scale_fill_viridis_c(direction = -1, 
    na.value = "#ffffff", option = "C") +
  interior_annotation("a") +
  xlim(sc_xlims) + ylim(sc_ylims)
```

@@

hex_grid_coloured_scurve2 <- ggplot() + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve2, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", 
        linewidth=0.2) +
  geom_point(data = umap_scurve_scaled,
           aes(x = UMAP1, y = UMAP2),
           alpha = 0.3,
           size = 0.5) +
  scale_fill_viridis_c(direction = -1, 
    na.value = "#ffffff", option = "C") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("b")

@@

hex_grid_coloured_scurve3 <-  ggplot() + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve3, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", linewidth=0.2) +
  geom_point(data = umap_scurve_scaled,
           aes(x = UMAP1, y = UMAP2),
           alpha = 0.3,
           size = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("c")

@@

hex_grid_rm_lwd_scurve1 <-  ggplot(
  data = hex_grid_with_counts_s_curve2, 
  aes(x = x, y = y)) + 
  geom_polygon(aes(group = hex_poly_id, fill = std_counts), 
            color = "grey70", linewidth=0.2) +
  geom_text(data = hex_grid_with_low_counts, 
            color = "black", 
            aes(x = c_x, y = c_y, group = hex_poly_id, label = "X", size = 1)) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("a")
```

@@

hex_grid_rm_lwd_scurve2 <-  ggplot(
  data = hex_grid_with_counts_s_curve2, 
  aes(x = x, y = y)) + 
  geom_polygon(aes(group = hex_poly_id, fill = std_counts), 
            color = "grey70", linewidth=0.2) +
  geom_text(data = hex_grid_with_low_counts_neighbor, 
            color = "black", 
            aes(x = c_x, y = c_y, group = hex_poly_id, label = "X", size = 1)) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("b")
```
